\section{Conclusion}
\label{sec:conclusion}
In this work, we presented and evaluated two approaches to reduce different types of uncertainty in diffusion MRI tractography. The first one, model averaging, relies on Bayesian model comparison, and reduces the model uncertainty in crossing fiber tractography that results from having to select the most suitable number of fibers in each tracking step. The second one, bootstrap consensus, primarily aims to reduce data uncertainty, but we observe that it also reduces model uncertainty due to an interdependency of both. In either case, we fuse information from multiple fiber estimates to obtain a more reliable basis for fiber tractography.

Our experimental results demonstrate that each of the two approaches by itself makes dMRI tractography more accurate, as confirmed both by qualitative results and a formal statistical analysis. Even though combining both methods yielded an additional benefit, in terms of practical utility, it is worth keeping in mind that the additional computational expense from model averaging is marginal (in our experiments, it added 20 seconds to the pre-processing), while the computational effort for bootstrapping is substantial (in our experiments, more than eight hours per dataset).

We expect that, in many use cases, this will make model averaging the more pragmatic choice. Despite this, bootstrapping also provided further insights, most importantly, on the interaction between data and model uncertainty, and the effect of model averaging on the uncertainty in fiber direction estimates.

\section*{Acknowledgments}

We thank Gemma van der Voort (University of Bonn) for her initial proof-of-concept implementation of tractography with model averaging, and for providing feedback on our manuscript. This work was funded by the Deutsche Forschungsgemeinschaft (DFG, German Research Foundation) -- 422414649.
Data were provided by the Human Connectome Project, WU-Minn Consortium (Principal Investigators: David Van Essen and Kamil Ugurbil; 1U54MH091657) funded by the 16 NIH Institutes and Centers that support the NIH Blueprint
for Neuroscience Research; and by the McDonnell Center for Systems Neuroscience at Washington University.

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../main"
%%% End:
