\section{Results}
\subsection{Data}
The proposed novel bootstrap consensus model is applied to the selection,
average and rank $3$ model. The CSD model got replaced by the rank $3$ model
because it was knocked off compared to the other models by dice score. Further,
the CSD used in the model is computational heavy, i.e. computation takes 4 times as long
as the $4$th order CSD which is used within this paper. This especially matters
because of the time intense bootstrap creation. 

To evaluate the proposed models, data from the Human
Connectome Project (HCP) is used \cite{HCP}. The diffusion MR images have a resolution of $1.25$ mm
isotropic with $145 \times 174 \times 145$ voxels. 

As reference data we use the high quality data, which was published within the
scope of the Tractseg paper \cite{WASSERTHAL2018239}. This reference data has been
created by manually refining the segmented full brain fiber tractography. For
more details we refer to the original literature.

All tests were performed on 12 randomly chosen subjects for which such reference tractographies
exist. Since these tractographies cannot be seen as ground truth and more as a
good reference, we are just interested how good the proposed approach manages to
reconstruct major white matter bundles. Therefore, we compare the approach by
Dice score, which is defined as
\[ 
	DICE = \frac{2 |RD \cap TR |}{|TR| + |RD|} ,
\]
where $RD$ denotes the reference data and $TR$ the tracking results
\cite{SCHILLING2019194}. 
Further, we measure how much is cut off the streamlines by the density filter.
This should indicate if the reconstruction is maybe good, however it is hardly
dependent on the applied filter. 

\subsection{Computational Effort}
All experiments were computed on an Intel i9 with 3.3 GHz and 64 GB RAM. The
following durations are denoted in h:min:s or min:s.

The computation of a single bootstrap data sample took 1:10 on a single core,
multi-threaded fourth order fODF estimation took 4:33, the computation of the
selection model took 1:10, the computation of the averaging model took 1:30 and
the computation of the rank-3 model 0:40. The calculation of 100 bootstraps took
therefore 8:08:00, using all threads to create the bootstrap data as well as the
models. This also includes the computation of the consensus model, which on its
own took 11:00. The tracking itself is independent of the preprocessing steps.
It took approximately 2:30 for a bundle such it is shown in Figure xy on a
single thread including postprocessing.  

\subsection{Qualitative Comparison}
As a first experiment we tracts the right Cortiscospinal Tract (CST) from a seed
region, which is indicated with a dashed black line in Fig. XY. 
